---
title: "R básico"
output: html_notebook
---

## Explicaciones de crear chunks y ejecutar el código

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r}
print(pi, 10)
```


```{r}
round(pi, 5)
```


```{r}
floor(pi)
```


```{r}

ceiling(pi)
```



***

## Variables y funciones

nombre_variables no utilizamos nombre de funciones reservadas 




```{r}
miVariable = 4
doble = function(x){
  2*x
}
# Para ejecutar en bloque MAY+CTRL+INTRO
```


```{r}
# Para reutilizar la función
doble(miVariable)
```


```{r}
cuadrado = function(x){x^2}
cuadrado(miVariable)
```





## Demostración de los chunks

```{r message=TRUE, echo = TRUE, warning=FALSE}
library(car)

head(cars,3) # mostramos las tres primeras líneas
```

```



## Estructura de datos

```{r}
primer_vector = c(1,2,3) # para declarar un vector
```



```{r}
segundo_vector = scan() # para definir un vector de forma manual
```



```{r}
fix(primer_vector) # cuando necesitamos modificar un vector x
```



```{r}
rep("RStudio", 6)# dado un objeto a, define un vector constante n veces
```



### Progresiones y secuencias

```{r}
seq(a,b, by=d) # from...to, by = incremento
```


```{r}
seq(a,b, length.out=n) # from ...to, progresión dada una longitud deseada n
```


```{r}
seq(a:b) # secuencia from...to números enteros consecutivos
```




## Funciones


```{r}
sapply(primer_vector, FUN=doble) # es el equivalente de un ciclo FOR ... LOOP
```


```{r}
# funciones nativas
sqrt(primer_vector)
```




















